Development of a permanent magnet characterisation framework for use in low-field MRI systems

### 2024-02-28 documentation/colloquium/presentation/index.qmd
Update index.qmd

<p class="fragment">&#x2022; Permanent magnets differ in their field strength due to their manufacturing process and environmental changes</p>
<p class="fragment">&#x2022; This influences the homogeneity of the assembled magnet</p>
<p class="fragment">&#x2022; It can be improved by means of a complex shimming process</p>

@@

<p class="fragment">&#x2022; Measure magnets in advance</p>
<p class="fragment">&#x2022; Execute optimization or sorting algorithms on the magnet field data</p>
<p class="fragment">&#x2022; Build an optimized magnet</p>

@@

## But

>>>>

<p class="fragment">&#x2022; Permanent magnets differ in their field strength due to the manufacturing process and environmental changes</p>
<p class="fragment">&#x2022; This influences the homogeneity of the assembled magnet</p>
<p class="fragment">&#x2022; It can be improved by means of a complex shimming process</p>

@@

<p class="fragment">&#x2022; Measure magnets in advance</p>
<p class="fragment">&#x2022; Execute optimisation or sorting algorithms on the magnetic field data</p>
<p class="fragment">&#x2022; Build an optimised magnet</p>

@@

## ... but
